Exploring United States Housing Affordability

### 2016-08-10 paper/Paper.Rmd
title changes

<br>
<br>
<br>

@@

#Graphical findings

@@

us_map %>% 
  ggplot() +  
  geom_polygon(aes(x=long, 
                   y = lat, 
                   fill = zinc2_median, 
                   group = group)) + 
  coord_fixed(1.3) +
  theme_tufte(base_size = 20, 
              base_family = "serif") +
  scale_x_continuous(name = NULL,
                     labels = NULL,
                     breaks = NULL) +
  scale_y_continuous(name = NULL,
                     labels = NULL,
                     breaks = NULL) +
  labs(fill = "Median income") +
  scale_fill_distiller(limits = c(35000, 54000), 
                                 breaks = sort(unique(us_map$zinc2_median),
                                               decreasing = T),
                                 palette = "Greens", 
                                 direction = 1,
                                 guide = "legend",
                        labels=function(x){paste0("$",
                                                  x %/% 100 / 10, "K")})
```
\begin{center}
Figure 2: Median Income Across Census Regions
\end{center}

>>>>

\vspace{72pt}

@@

#Findings

@@

us_map %>% 
  ggplot() +  
  geom_polygon(aes(x=long, 
                   y = lat, 
                   fill = zinc2_median, 
                   group = group)) + 
  coord_fixed(1.3) +
  theme_tufte(base_size = 14, 
              base_family = "serif") +
  scale_x_continuous(name = NULL,
                     labels = NULL,
                     breaks = NULL) +
  scale_y_continuous(name = NULL,
                     labels = NULL,
                     breaks = NULL) +
  labs(fill = "Median income") +
  scale_fill_distiller(limits = c(35000, 54000), 
                                 breaks = sort(unique(us_map$zinc2_median),
                                               decreasing = T),
                                 palette = "Greens", 
                                 direction = 1,
                                 guide = "legend",
                        labels=function(x){paste0("$",
                                                  x %/% 100 / 10, "K")})
```
\begin{center}
Figure 2: Median Income Across Census Regions
\end{center}
